---
title: "COVID-19"
subtitle: "How does it compare?"
always_allow_html: yes
output:
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, eval = T, error = F, cache = F)
```

```{r loads}
# Install and load pacman if not already installed
if (!require("pacman")) install.packages("pacman")
library(pacman)

p_load(tidyverse,magrittr, #general cleaning and piping
       stringr, #string manipulation
       lubridate, #I hate dates
       feather,#nimble files
       DataExplorer, #check missings
       ggplot2,plotly, #gen viz
       sf,mapview,#maps
       prettydoc,
       zoo) #rmd layout

#load data
flu <- read_csv("data/cdc_data/influenza_VirusViewByWeek.csv")
names(flu) = c("year","week","virus","z_4","five_24","twofive_sixfour","sixfive_up")
covid_pop_df <- read_feather("data/covid_pop.feather")
```


<center>
Erin Wright
</center>

---

```{r}
#format flu data
flu_df <- flu %>% 
  gather(key,value,z_4:sixfive_up) %>%
  group_by(year,week) %>%
  summarise(total_flu_cases = sum(value)) %>%
  ungroup() %>%
  filter(year >= year(Sys.Date())-1) %>%
  arrange(year,week) %>%
  group_by(year) %>%
  mutate(cum_cases = cumsum(total_flu_cases)) %>%
  select(-total_flu_cases) %>%
  spread(year,cum_cases) %>%
  rename(Flu_2020 = `2020`,
         Flu_2019 = `2019`)
#format covid data
covid_flu <- covid_pop_df %>%
  filter(country_region == "US") %>%
  select(ctry_cnfrm,week) %>%
  mutate(week = as.numeric(week)) %>%
  group_by(week) %>%
  mutate(confirmed = max(ctry_cnfrm)) %>%
  distinct() %>%
  full_join(flu_df, by = c("week")) %>%
  arrange(week) %>%
  #this data looks WRONG so...smoothing it
  #mutate(confirmed = case_when(week %in% c(13,14) ~ NA_integer_,
  #                             TRUE ~ as.integer(confirmed))) %>%
  ungroup() %>%
  rename(`COVID-19` = ctry_cnfrm) 
rm(flu_df)

```


# Confirmed Cases (US)

## Influenza^[Data Source: https://gis.cdc.gov/grasp/fluview/flu_by_age_virus.html]

### Is the trend of cumulative confirmed *COVID-19*^[Data Source: https://github.com/CSSEGISandData/COVID-19] cases really higher than that of *Influenza*?

<center>
```{r}

fig1 <- plot_ly(covid_flu, x = ~week, y = ~Flu_2019,name = "Influenza (2019)", type = 'scatter', mode = 'lines',line = list(color = 'grey', width = 2)) 
fig1 <- fig1 %>% add_trace(y = ~`COVID-19`, name = 'COVID-19 (2020)', mode = 'lines',connectgaps = TRUE,line = list(color = 'red', width = 4)) 
fig1 <- fig1 %>% add_trace(y = ~Flu_2020, name = 'Influenza (2020)', mode = 'lines',line = list(color = 'blue', width = 4))
fig1 <- fig1 %>% layout(title = "Confirmed Cases by Week of Year (USA)",
         xaxis = list(title = "Week Number"),
         yaxis = list (title = "# of Confirmed Cases")
         #paper_bgcolor = 'transparent',
         #plot_bgcolor = 'transparent',
         )

fig1
```
</center>

# Cause of Death (US)

## How does the reported COVID-19 data compare to other causes of death?^[Data Source: https://www.cdc.gov/nchs/pressroom/stats_of_the_states.htm]

```{r}
#read in several more 
cancer <- read_csv("data/cdc_data/cancer_mortality_state.csv", skip = 2) %>% filter(YEAR == max(YEAR)) %>% select(-URL) %>% summarise(deaths = sum(DEATHS),cause = "Cancer")
firearm <- read_csv("data/cdc_data/firearm_mortality_state.csv", skip = 2) %>% filter(YEAR == max(YEAR)) %>% select(-URL)%>% summarise(deaths = sum(DEATHS),cause = "Firearms")
diabetes <- read_csv("data/cdc_data/diabetes_mortality_state.csv", skip = 2) %>% filter(YEAR == max(YEAR)) %>% select(-URL)%>% summarise(deaths = sum(DEATHS),cause = "Diabetes")
heart_dis <- read_csv("data/cdc_data/heart_disease_mortality_state.csv", skip = 2) %>% filter(YEAR == max(YEAR)) %>% select(-URL)%>% summarise(deaths = sum(DEATHS),cause = "Heart Disease")
flu_pne <- read_csv("data/cdc_data/influenza_pneumonia_mortality_state.csv", skip = 2) %>% filter(YEAR == max(YEAR)) %>% select(-URL)%>% summarise(deaths = sum(DEATHS),cause = "Flu/Pneumonia")
suicide <- read_csv("data/cdc_data/suicide_mortality_state.csv", skip = 2) %>% filter(YEAR == max(YEAR)) %>% select(-URL)%>% summarise(deaths = sum(DEATHS),cause = "Suicide")
covid_other_deaths <- covid_pop_df %>% 
  filter(country_region == "US") %>%
  mutate(deaths = max(ctry_deaths),
            cause = "COVID-19",
            pop2018 = country_pop2018) %>%
  select(deaths,cause,pop2018) %>%
  distinct() %>%
  union_all(cancer) %>%
  union_all(firearm) %>%
  union_all(diabetes) %>%
  union_all(heart_dis) %>%
  union_all(flu_pne) %>%
  union_all(suicide) %>%
  mutate(pop2018 = na.locf(pop2018,fromLast = TRUE),
         deaths_rate = deaths/(pop2018/100000))

rm(list = c("cancer","diabetes","firearm",
            "heart_dis","flu_pne","suicide"))

```

Consideration must be given to the fact that COVID-19 data only represents a portion of a year whereas the other causes have all data from 2018 included.  Data was adjusted to represent rates per 100,000 population^[Data Source: https://data.worldbank.org/indicator/sp.pop.totl].  To do this the total number of deaths was divided by the number of groups of 100,000 persons present in the population using the 2018 US population estimate of `r paste0(covid_other_deaths$pop2018[1])`.


```{r}
#COMPARE DEATHS HERE to other death things like cancer etc. 
fig2 <- plot_ly(covid_other_deaths, x = ~cause, y = ~deaths_rate,name = "Deaths per 100,000 people", type = 'bar', mode = 'group',
                            marker = list(color = c(
                                    "blue",
                                    "grey",
                                    "grey",
                                    "grey",
                                    "grey",
                                    "grey",
                                    "grey")))
fig2 <- fig2 %>% layout(title = "Deaths per 100,000 people (US)",
        xaxis = list(title = "Cause"),
        yaxis = list (title = "Death Rate"))

```

<center>
```{r}
fig2
```
</center>

Since COVID-19 has been accumulating over less than a year, what if we calculate the death rate using both population and days accumulating? So if we take the death rate calculated above then multiply by the fraction of a year represented by the data, it might be closer to a far comparison;*for other than COVID-19 this would be just 1, for COVID-19 this would be 365 divided by virus days passed.*

```{r}
cancer <- read_csv("data/cdc_data/cancer_mortality_state.csv", skip = 2) %>% filter(YEAR == max(YEAR)) %>% select(-URL) %>% summarise(deaths = sum(DEATHS),cause = "Cancer",day_virus = 365)
firearm <- read_csv("data/cdc_data/firearm_mortality_state.csv", skip = 2) %>% filter(YEAR == max(YEAR)) %>% select(-URL)%>% summarise(deaths = sum(DEATHS),cause = "Firearms",day_virus = 365)
diabetes <- read_csv("data/cdc_data/diabetes_mortality_state.csv", skip = 2) %>% filter(YEAR == max(YEAR)) %>% select(-URL)%>% summarise(deaths = sum(DEATHS),cause = "Diabetes",day_virus = 365)
heart_dis <- read_csv("data/cdc_data/heart_disease_mortality_state.csv", skip = 2) %>% filter(YEAR == max(YEAR)) %>% select(-URL)%>% summarise(deaths = sum(DEATHS),cause = "Heart Disease",day_virus = 365)
flu_pne <- read_csv("data/cdc_data/influenza_pneumonia_mortality_state.csv", skip = 2) %>% filter(YEAR == max(YEAR)) %>% select(-URL)%>% summarise(deaths = sum(DEATHS),cause = "Flu/Pneumonia",day_virus = 365)
suicide <- read_csv("data/cdc_data/suicide_mortality_state.csv", skip = 2) %>% filter(YEAR == max(YEAR)) %>% select(-URL)%>% summarise(deaths = sum(DEATHS),cause = "Suicide",day_virus = 365)


covid_other_deaths2 <- covid_pop_df %>% 
  filter(country_region == "US") %>%
  mutate(deaths = max(ctry_deaths),
            cause = "COVID-19",
            pop2018 = country_pop2018) %>%
  select(deaths,cause,pop2018,day_virus) %>%
  filter(day_virus == max(day_virus)) %>%
  distinct()%>% 
  union_all(cancer) %>%
  union_all(firearm) %>%
  union_all(diabetes) %>%
  union_all(heart_dis) %>%
  union_all(flu_pne) %>%
  union_all(suicide) %>%
  mutate(pop2018 = na.locf(pop2018,fromLast = TRUE),
         deaths_rate = (deaths/(pop2018/100000))*(365/day_virus))

rm(list = c("cancer","diabetes","firearm",
            "heart_dis","flu_pne","suicide"))

```

<center>
```{r}
#COMPARE DEATHS HERE to other death things like cancer etc. 
fig2_2 <- plot_ly(covid_other_deaths2, x = ~cause, y = ~deaths_rate,name = "", type = 'bar', mode = 'group',
                            marker = list(color = c(
                                    "blue",
                                    "grey",
                                    "grey",
                                    "grey",
                                    "grey",
                                    "grey",
                                    "grey")))
fig2_2 <- fig2_2 %>% layout(title = "Deaths Rate per 100,000 people (US) for Days Accumulated",
        xaxis = list(title = "Cause"),
        yaxis = list (title = "Death Rate"))

fig2_2
```
</center>

# Locations

## Where was the first report in each country?

<center>
```{r}
covid_routes <- covid_pop_df %>%
  filter(day_virus == 1) %>% #day 1 would be the first day the virus landed in a country
  select(country_region,day_virus,lat,lon) %>% 
  group_by(country_region) %>%
  mutate(lat = mean(lat),
         lon = mean(lon)) %>%
  distinct() %>% 
  ungroup() %>%
  mutate(from_lat = lat,
         to_lat = lead(from_lat,1),
         from_lon = lon,
         to_lon = lead(lon,1),
         #jitter slightly so that not identical for route map
         from_lat = jitter(from_lat, factor = 0.1),
         from_lon = jitter(from_lon, factor = 0.1),
         to_lat = jitter(to_lat, factor = 0.1),
         to_lon = jitter(to_lon, factor = 0.1))

#https://rstudio-pubs-static.s3.amazonaws.com/259095_2f8cb24b43284692a8af916bd447931d.html
map_setup <- borders("world", colour="grey80", fill="grey3")
virus_travel <- ggplot() + map_setup +
  geom_curve(data=covid_routes,
             aes(x=from_lon, y=from_lat, xend=to_lon, yend=to_lat),
             col="darkblue",
             size=.5,
             curvature=0.2) +
  geom_point(data=covid_routes,
             aes(x=from_lon, y=from_lat), 
             colour="blue",
             size=1.5) +
  geom_point(data=covid_routes,
             aes(x=to_lon, y=to_lat), 
             colour="blue") +
  theme(axis.line=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.ticks=element_blank(),
        plot.title=element_text(hjust=0.5, size=12)) +
  ggtitle("COVID-19 First Reported Appearances in Each Country")# +
#check the min/max of long and lat to get good zoom level if needed or leave out
#coord_cartesian(ylim=c(10, 75), xlim=c(-160, 70))
ggplotly(virus_travel)

```
</center>


## Where did it spread

This gets a little busy, but is still very neat to look at; if we take the first location the virus is known to have landed (confirmed cases) in each country, and follow it country:country we get this:

<center>
```{r}
virus_travel
```
</center>



# How fast did it spread?

Day of Virus represents the first day a reported case is docuemnted for each country listed.

```{r}
covid_pop_v1 <- covid_pop_df %>% 
  select(country_region, day_virus,perc_ctry_cnfrm) %>% 
  filter(country_region %in% c("US","Italy","China","Germany","Switzerland","Ireland","Sweden","United Kingdom")) %>% 
  mutate(row_id = row_number(),
         perc_ctry_cnfrm = as.numeric(perc_ctry_cnfrm)) %>%
  group_by(day_virus) %>%
  spread(country_region,perc_ctry_cnfrm) %>%
  select(-row_id) %>%
  distinct() %>%
  mutate_all(as.numeric)

CH = covid_pop_v1 %>% select(day_virus,China) %>% filter(!is.na(China))
G = covid_pop_v1 %>% select(day_virus,Germany) %>% filter(!is.na(Germany))
IT = covid_pop_v1 %>% select(day_virus,Italy) %>% filter(!is.na(Italy))
IR = covid_pop_v1 %>% select(day_virus,Ireland) %>% filter(!is.na(Ireland))
ST = covid_pop_v1 %>% select(day_virus,Switzerland) %>% filter(!is.na(Switzerland))
SW = covid_pop_v1 %>% select(day_virus,Sweden) %>% filter(!is.na(Sweden))
UK = covid_pop_v1 %>% select(day_virus,`United Kingdom`) %>% filter(!is.na(`United Kingdom`))
US = covid_pop_v1 %>% select(day_virus,US) %>% filter(!is.na(US))

covid_pop_v1 <- CH %>%
  full_join(G,by = "day_virus") %>%
  full_join(IT,by = "day_virus") %>%
  full_join(IR,by = "day_virus") %>%
  full_join(ST,by = "day_virus") %>%
  full_join(SW,by = "day_virus") %>%
  full_join(UK,by = "day_virus") %>%
  full_join(US,by = "day_virus") 
```


<center>
```{r}
# thinking to put line chart with lines for each country, but day and maybe y = confirmed cases

fig3 <- plot_ly(covid_pop_v1, x = ~day_virus, y = ~China,name = "China", type = 'scatter', mode = 'line',line = list(color = 'black', width = 2))
fig3 <- fig3 %>% add_trace(y = ~Germany, name = "Germany", mode = 'line',line = list(color = 'yellow', width = 2))
fig3 <- fig3 %>% add_trace(y = ~Ireland, name = "Ireland", mode = 'line',line = list(color = 'orange', width = 2))
fig3 <- fig3 %>% add_trace(y = ~Italy, name = "Italy", mode = 'line',line = list(color = 'green', width = 2))
fig3 <- fig3 %>% add_trace(y = ~Sweden, name = "Sweden", mode = 'line',line = list(color = 'red', width = 2))
fig3 <- fig3 %>% add_trace(y = ~Switzerland, name = "Switzerland", mode = 'line',line= list(color = 'pink', width = 2))
fig3 <- fig3 %>% add_trace(y = ~`United Kingdom`, name = "United Kingdom", mode = 'line',line= list(color = 'purple', width = 2))
fig3 <- fig3 %>% add_trace(y = ~US, name = "United States", mode = 'line',line = list(color = 'blue', width = 2))
fig3 <- fig3 %>% layout(title = "Confirmed Cases by Virus Day",
                  xaxis = list(title = "Day of Virus"),
                  yaxis = list (title = "% Country Population Confirmed"))

fig3
```
</center>

# Country Populations

## How does the reported COVID-19 data compare across the globe?

When taking into account the overall population of each of the following countries, what is the impact for each?^[Data Source: https://data.worldbank.org/indicator/sp.pop.totl].


```{r}
covid_pop_v2 <- covid_pop_df %>% group_by(country_region,day_virus) %>%  gather(case_type,perc_cases,perc_ctry_cnfrm:perc_ctry_dead) %>% 
  select(country_region, day_virus,perc_cases,case_type) %>% 
  filter(country_region %in% c("US","Italy","China","Germany","Switzerland","Ireland","Sweden","United Kingdom")) %>% 
  mutate(perc_cases = as.numeric(perc_cases)) %>%
  group_by(country_region) %>%
  filter(day_virus == max(day_virus)) %>%
  distinct()
```


<center>
```{r}
fun_bar3 <- function(df,x_var,y_var,color_var,color_varName,stacked=T,horizontal=F,...) {
  
  library(magrittr)
  plot_ly(
    x = ~x_var,
    y = ~y_var,
    color = ~as.character(color_var),
    colors = c("blue","red","green")
  ) %>%
    add_bars() %>%
    layout(
      barmode = ifelse(stacked,'stack','group'),
      orientation = ifelse(horizontal,'h','v'),    
      title = paste0("COVID-19 by ",color_varName),
      xaxis = list(title = "", tickangle = 45),
      yaxis = list(title = "Percent")
    )
}

fun_bar3(covid_pop_v2,covid_pop_v2$country_region,covid_pop_v2$perc_cases,covid_pop_v2$case_type,"% of Country Total Population (2018)",stacked = F)

```
</center>


```{r}
#age data
cia_med_age <- read_table("https://www.cia.gov/library/publications/the-world-factbook/rankorder/rawdata_2177.txt",col_names = F, skip = 1)
names(cia_med_age) = c("row_id","country","country2","country3","age")
cia_med_age <- cia_med_age %>% 
  mutate(country = paste0(country," ",country2," ",country3) %>% str_trim()) %>%
  select(country,age) %>%
  filter(country %in% c("United States","Italy","China","Germany","Switzerland","Ireland","Sweden","United Kingdom")) %>%
  mutate( country = recode(country,"United States" = "US")) %>%
  distinct() %>%
  arrange(country)
  

```

## What about age?^[Data Source: https://www.cia.gov/library/publications/the-world-factbook/]

```{r}
covid_pop_v3 <- covid_pop_df %>% 
  select(country_region, day_virus,perc_ctry_dead) %>% 
  filter(country_region %in% c("US","Italy","China","Germany","Switzerland","Ireland","Sweden","United Kingdom")) %>% 
  mutate(row_id = row_number(),
         perc_ctry_dead = as.numeric(perc_ctry_dead)) %>%
  group_by(day_virus) %>%
  spread(country_region,perc_ctry_dead) %>%
  select(-row_id) %>%
  distinct() %>%
  mutate_all(as.numeric)

CH = covid_pop_v3 %>% select(day_virus,China) %>% filter(!is.na(China))
G = covid_pop_v3 %>% select(day_virus,Germany) %>% filter(!is.na(Germany))
IT = covid_pop_v3 %>% select(day_virus,Italy) %>% filter(!is.na(Italy))
IR = covid_pop_v3 %>% select(day_virus,Ireland) %>% filter(!is.na(Ireland))
ST = covid_pop_v3 %>% select(day_virus,Switzerland) %>% filter(!is.na(Switzerland))
SW = covid_pop_v3 %>% select(day_virus,Sweden) %>% filter(!is.na(Sweden))
UK = covid_pop_v3 %>% select(day_virus,`United Kingdom`) %>% filter(!is.na(`United Kingdom`))
US = covid_pop_v3 %>% select(day_virus,US) %>% filter(!is.na(US))

covid_pop_v3 <- CH %>%
  full_join(G,by = "day_virus") %>%
  full_join(IT,by = "day_virus") %>%
  full_join(IR,by = "day_virus") %>%
  full_join(ST,by = "day_virus") %>%
  full_join(SW,by = "day_virus") %>%
  full_join(UK,by = "day_virus") %>%
  full_join(US,by = "day_virus") 

```


<center>
```{r}
# thinking to put line chart with lines for each country, but day and maybe y = confirmed cases

fig4 <- plot_ly(covid_pop_v3, x = ~day_virus, y = ~China,name = "China", type = 'scatter',mode = 'line',line = list(color = 'black', width = 2))
fig4 <- fig4 %>% add_trace(y = ~Germany, name = "Germany", mode =  'line',line = list(color = 'yellow', width = 2))
fig4 <- fig4 %>% add_trace(y = ~Ireland, name = "Ireland", mode = 'line',line = list(color = 'orange', width = 2))
fig4 <- fig4 %>% add_trace(y = ~Italy, name = "Italy", mode = 'line',line = list(color = 'green', width = 2))
fig4 <- fig4 %>% add_trace(y = ~Sweden, name = "Sweden", mode = 'line',line = list(color = 'red', width = 2))
fig4 <- fig4 %>% add_trace(y = ~Switzerland, name = "Switzerland", mode = 'line',line = list(color = 'pink', width = 2))
fig4 <- fig4 %>% add_trace(y = ~`United Kingdom`, name = "United Kingdom", mode = 'line',line = list(color = 'purple', width = 2))
fig4 <- fig4 %>% add_trace(y = ~US, name = "United States", mode = 'line',line = list(color = 'blue', width = 2))

subfig4 <- plot_ly(
  type = 'table',
  domain = list(x=c(0,0.3), y=c(0.3,0.3)),
  header = list(values = c("country", "age")),
  cells = list(values = rbind(cia_med_age$country,cia_med_age$age))
)

fig4 <- fig4 %>% layout(title = "Deaths by Virus Day for % Country Population (Median Country Age shown in table)",
                  xaxis = list(title = "Day of Virus"),
                  yaxis = list (title = "# of Deaths"),
                  yaxis2 = list(overlaying = "y", side = "right"))

subplot(fig4, subfig4) %>%
  layout(xaxis = list(domain=c(0.75,0.5)),
         xaxis2 = list(domain=c(0,0.5)))

```
</center>

### Is the country median age related to the total cumulative deaths for % country population?

<center>
```{r}
covid_pop_v4 <- covid_pop_df %>% 
  select(country_region, perc_ctry_dead) %>% 
  filter(country_region %in% c("US","Italy","China","Germany","Switzerland","Ireland","Sweden","United Kingdom")) %>% 
  mutate(perc_ctry_dead = as.numeric(perc_ctry_dead)) %>%
  rename(country = "country_region") %>%
  group_by(country) %>%
  filter(perc_ctry_dead == max(perc_ctry_dead)) %>%
  mutate(perc_ctry_dead = perc_ctry_dead) %>%
  distinct() %>%
  mutate_all(as.numeric) %>%
  left_join(cia_med_age,by = "country") %>%
  mutate(age = age)
  
fig5 <- plot_ly(covid_pop_v4, x = ~perc_ctry_dead, y = ~age, type = 'scatter',mode = 'markers', color = ~country,colors = c("black","yellow","orange","green","red","pink","purple","blue"))
fig5 <- fig5 %>% layout(title = "Age vs % Total Population Dead",
                  xaxis = list(title = "% dead"),
                  yaxis = list (title = "age"),
                  yaxis2 = list(overlaying = "y", side = "right"))
fig5 
```
</center>

<br>
<br>

<center>
```{r}
covid_pop_v4 <- covid_pop_df %>% 
  select(country_region, perc_ctry_dead) %>% 
  filter(country_region %in% c("US","Italy","China","Germany","Switzerland","Ireland","Sweden","United Kingdom")) %>% 
  mutate(perc_ctry_dead = as.numeric(perc_ctry_dead)) %>%
  rename(country = "country_region") %>%
  group_by(country) %>%
  filter(perc_ctry_dead == max(perc_ctry_dead)) %>%
  mutate(perc_ctry_dead = log(perc_ctry_dead)) %>%
  distinct() %>%
  mutate_all(as.numeric) %>%
  left_join(cia_med_age,by = "country") %>%
  mutate(age = log(age))
  
fig5 <- plot_ly(covid_pop_v4, x = ~perc_ctry_dead, y = ~age, type = 'scatter',mode = 'markers', color = ~country,colors = c("black","yellow","orange","green","red","pink","purple","blue"))
fig5 <- fig5 %>% layout(title = "Age vs % Total Population Dead",
                  xaxis = list(title = "log(% dead)"),
                  yaxis = list (title = "(logage)"),
                  yaxis2 = list(overlaying = "y", side = "right"))
fig5 
```
</center>



# Credits

I used these sources to build the graphics in this report:

* Maps: https://rstudio-pubs-static.s3.amazonaws.com/259095_2f8cb24b43284692a8af916bd447931d.html
* Plotly in R: https://plotly.com/r/line-charts/ 
* Sub Plots: https://stackoverflow.com/questions/56267164/r-plotly-subplot-with-table

<div style="position: fixed; bottom: 15px; right:10px;">
  <div id="feedback"><a href="https://github.com/cluelessgumshoe/explore_covid"> <B>SOURCE CODE</B></a></div>
</div>

<small><i>Report Date: `r Sys.Date()`</i>